%!TEX root = ../study_diagram.tex

\begin{studyplan}[
  programme={Mekanik},
  name={Noah R. B. Hansen},
  heading left={STUDIE},
  heading right={DIAGRAM $\cdot$ MEKANIK},
  degree={Bacheloruddannelsen i mekanik},
  show legend=true,
  show header=true
]
  \begin{semester}[Sep. 2024 -- Jan. 2025]{\StudyDiagramText{1. semester}{1st semester}}
    \course[type=obligatory,status=completed,grade={7}]{5}{\StudyDiagramText{Design og konstruktion}{Design and Construction}}
    \course[type=obligatory,status=completed,grade={12}]{5}{\StudyDiagramText{Programmering og numeriske metoder}{Programming and Numerical Methods}}
    \course[type=obligatory,status=completed,grade={12}]{10}{\StudyDiagramText{Fysik og mekanik}{Physics and Mechanics}}
    \course[type=obligatory,status=completed,grade={10}]{10}{\StudyDiagramText{Calculus tau}{Calculus tau}}
  \end{semester}

  \begin{semester}[Feb. 2025 -- Jun. 2025]{\StudyDiagramText{2. semester}{2nd semester}}
    \course[type=obligatory,status=completed,grade={12}]{10}{\StudyDiagramText{Termodynamik og energisystemer}{Thermodynamics and Energy Systems}}
    \course[type=obligatory,status=completed,grade={12}]{10}{\StudyDiagramText{Materialelære}{Materials Science}}
    \course[type=obligatory,status=completed,grade={10}]{10}{\StudyDiagramText{Ordinære differentialligninger, lineær algebra og vektorkalkulus}{Ordinary Differential Equations, Linear Algebra and Vector Calculus}}
  \end{semester}

  \begin{semester}[Sep. 2025 -- Jan. 2026]{\StudyDiagramText{3. semester}{3rd semester}}
    \course[type=obligatory,status=completed,grade={10}]{10}{\StudyDiagramText{Statik og styrkelære}{Statics and Strength of Materials}}
    \course[type=obligatory,status=completed,grade={10}]{10}{\StudyDiagramText{Fluidmekanik}{Fluid Mechanics}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Dynamik og vibrationer}{Dynamics and Vibrations}}
    \course[type=obligatory,status=completed,grade={7}]{5}{\StudyDiagramText{Partielle differentialligninger}{Partial Differential Equations}}
  \end{semester}

  \begin{semester}[Feb. 2026 -- Jun. 2026]{\StudyDiagramText{4. semester}{4th semester}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Kontrolteori}{Control Theory}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Elektromagnetisme og elektronik}{Electromagnetism and Electronics}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Elasticitetsteori}{Elasticity Theory}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Maskinelementer}{Machine Elements}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Statistik og eksperimentelle metoder}{Statistics and Experimental Methods}}
    \course[type=obligatory,status=current,grade={}]{5}{\StudyDiagramText{Numerisk analyse for ingeniører}{Numerical Analysis for Engineers}}
  \end{semester}

  \begin{semester}[Sep. 2026 -- Jan. 2027]{\StudyDiagramText{5. semester}{5th semester}}
    \course[type=obligatory,status=planned,grade={}]{5}{\StudyDiagramText{Varmetransmission}{Heat Transfer}}
    \course[type=obligatory,status=planned,grade={}]{5}{\StudyDiagramText{Fremstillingsprocesser}{Manufacturing Processes}}
    \course[type=elective,status=planned,grade={}]{10}{\StudyDiagramText{Udviklingsprojekt i Mekanik}{Development Project in Mechanics}}
    \course[type=elective,status=planned,grade={}]{5}{\StudyDiagramText{Finite element- og mekanisme-analyse}{Finite element and mechanism analysis}}
    \course[type=elective,status=planned,grade={}]{5}{\StudyDiagramText{Kompositmaterialer}{Composite materials}}
  \end{semester}

  \begin{semester}[Feb. 2027 -- Jun. 2027]{\StudyDiagramText{6. semester}{6th semester}}
    \course[type=obligatory,status=planned,grade={}]{15}{\StudyDiagramText{Bachelorprojekt i mekanik}{Bachelor's Project in Mechanical Engineering}}
    \course[type=obligatory,status=planned,grade={}]{5}{\StudyDiagramText{Ingeniørvidenskabernes videnskabsteori og etik}{Philosophy of Science and Ethics for Engineering}}
    \course[type=elective,status=planned,grade={}]{5}{\StudyDiagramText{Valgfrie kurser}{Elective Courses}}
    \course[type=elective,status=planned,grade={}]{5}{\StudyDiagramText{Topology optimization}{Topology optimization}}
  \end{semester}
\end{studyplan}

\par\vspace{0.25cm}

\begin{studyplan}[
  programme={Mekanik},
  degree={Kandidatuddannelsen i mekanik og teknologi},
  show legend=false,
  show header=false,
  section title={Kandidatuddannelsen i mekanik og teknologi}
]
  \begin{semester}[Sep. 2027 -- Jan. 2028]{\StudyDiagramText{1. semester}{1st semester}}
    \course[type=obligatory,status=planned,grade={}]{5}{\StudyDiagramText{Datavidenskab}{Data Science}}
    \course[type=elective,status=planned,grade={}]{20}{\StudyDiagramText{Studielinjer}{Specialisation Tracks}}
    \course[type=elective,status=planned,grade={}]{5}{\StudyDiagramText{Valgfrie kurser}{Elective Courses}}
  \end{semester}

  \begin{semester}[Feb. 2028 -- Jun. 2028]{\StudyDiagramText{2. semester}{2nd semester}}
    \course[type=obligatory,status=planned,grade={}]{5}{\StudyDiagramText{Seminarrække}{Seminar Series}}
    \course[type=elective,status=planned,grade={}]{20}{\StudyDiagramText{Studielinjer}{Specialisation Tracks}}
    \course[type=elective,status=planned,grade={}]{5}{\StudyDiagramText{Valgfrie kurser}{Elective Courses}}
  \end{semester}

  \begin{semester}[Sep. 2028 -- Jan. 2029]{\StudyDiagramText{3. semester}{3rd semester}}
    \course[type=elective,status=planned,grade={}]{30}{\StudyDiagramText{Valgfrie kurser}{Elective Courses}}
  \end{semester}

  \begin{semester}[Feb. 2029 -- Jun. 2029]{\StudyDiagramText{4. semester}{4th semester}}
    \course[type=obligatory,status=planned,grade={}]{30}{\StudyDiagramText{Speciale i mekanik}{Master's Thesis in Mechanical Engineering}}
  \end{semester}
\end{studyplan}

\par\vspace{0.18cm}
\input{study_diagram/note.tex}
