
%!TEX TS-program = pdflatex
%!TEX encoding = UTF-8 Unicode
\documentclass[10pt,a4paper]{article}

\usepackage{resume/resume-style}

\begin{document}
\pagenumbering{gobble}

\resumeheader

\noindent
\begin{minipage}[t]{\sidewidth}
  \vspace{0pt}
  \colorbox{CVSidebar}{%
  \begin{minipage}[t][22.50cm][t]{\dimexpr\sidewidth-2\fboxsep\relax} %length
  \vspace{-10pt} %top space
  \hspace{3mm}% %padding left
  \begin{minipage}[t]{\dimexpr\linewidth-6mm\relax} %padding right
    \RaggedRight %left-aligned
    \small       %small font
    \sideheading{user}{Profile}
    Mechanical engineering student with a strong analytical mindset and experience with complex technical systems, reliability, structured problem-solving, technical documentation, data analysis, and troubleshooting. Comfortable working across hardware, software, and physical systems.

    \sideheading{graduation-cap}{Education}
    \textbf{BSc in Engineering\\(Mechanical Engineering)}\par
    Aarhus University\par
    \muted{Aarhus, Denmark}\hfill\cvdate{Aug. 2024 -- Present}\par
    \begin{itemize}
      \item Member of the Education Committee.
      \item Provisional GPA: 10.5
    \end{itemize}

    \vspace{3pt}{\color{CVBlueRule}\rule{\linewidth}{0.4pt}}\vspace{5pt}

    \textbf{HTX -- Mat A/Fys A}\par
    Vejle Tekniske Gymnasium\par
    \muted{Vejle, Denmark}\hfill\cvdate{Aug. 2020 -- Jun. 2023}\par
    \begin{itemize}
      \item Board member of the student council.
      \item Highest average grade in the nation; weighted GPA: 12.6.
    \end{itemize}

    \sideheading{trophy}{Selected achievements}
    \begin{itemize}
      \item Highest weighted GPA in the nation (2023)
      \item Danish Physics Olympiad national final qualification (2022)
      \item Georg Mohr competition winner seminar attendee (2022)
      \item Honourable mention, Projekt Forskerspirer (2022)
    \end{itemize}

    \sideheading{cogs}{Skills}
    \sideitem{Technical}{Electromechanical troubleshooting, DC motors, gearboxes, drivetrains, pumps, sensors, maintenance}
    \sideitem{Materials \& testing}{Four-point probe measurements, cryogenic handling, experimental data analysis}
    \sideitem{Tools}{AutoCAD, Solidworks, EES, MDSolids, Mathcad, LaTeX, MS Office, Inkscape}
    \sideitem{Programming}{Python, MATLAB, Lua, scripting}
    \sideitem{Languages}{Danish (native), English (C2), German (B1)}
  \end{minipage}%
  \end{minipage}%
  }
\end{minipage}%
\hspace{\gapwidth}%
\begin{minipage}[t]{\mainwidth}
  \vspace{0pt}
  \RaggedRight
  \small

  \begin{connectedsection}{briefcase}{14.20}{3,9,12.65}{Work Experience}
    \vspace{-10pt}\par
    \workentry
      {Maintenance Assistant, LEGOLAND}
      {Dec. 2023 -- Dec. 2025}
      {Billund, Denmark}
      {
        \begin{itemize}
          \item Performed independent electromechanical troubleshooting and maintenance on 24 V mobility-scooter-based electric vehicles used in LEGOLAND’s traffic school.
          \item Completed full overhaul/restoration work on approximately 18 traffic school cars, including DC motor refurbishment, brush replacement, gearbox servicing, brake/speeder adjustment, bushings, wheels, and fiberglass bodywork.
          \item Maintained Miniland animations involving 12 V DC motors, gearboxes, charging wires, PCBs, sensors, batteries, drivetrain tolerances, belts, chain drives, pumps, and fuse boxes.
          \item Diagnosed recurring failure on a controllable Femern Belt crane animation and developed a reset procedure; proposed a welded spool-guide modification that substantially reduced repeat faults on the crane and sister crane.
          \item Supported daily operation of Miniland by monitoring faults, restarting systems, and ensuring mechanical/electrical attractions remained operational.
        \end{itemize}
      }
      {yes}

    \workentry
      {Facility Assistant, LEGOLAND}
      {Jun. -- Dec. 2022 \& Aug. -- Dec. 2023}
      {Billund, Denmark}
      {
        \begin{itemize}
          \item Inspected approximately 193 technical rooms and infrastructure areas using digital checklists, creating work orders directly when issues could not be resolved on site.
          \item Supported safety and fire-compliance improvements by identifying deviations, following up on work orders, and helping ensure technical rooms met updated standards.
          \item Installed and dismantled approximately 400 outdoor wash lights for seasonal Christmas lighting, with attention to weatherproof cable routing and prevention of water ingress.
        \end{itemize}
      }
      {yes}

    \workentry
      {Tutor, Syddansk Erhvervsskole}
      {Aug. 2021 -- Jun. 2023}
      {Vejle, Denmark}
      {
        \begin{itemize}
          \item Provided peer tutoring as a part of the schools homework cafe.
        \end{itemize}
      }
      {}
  \end{connectedsection}

  \vspace{-10pt}

  \begin{connectedcontinued}{flask}{8.1}{1.1,3.3,5.1,7.2}{Projects \& Research}
    \vspace{-10pt}\par
    \projectentry{YBCO superconductors project}
      {Investigated high-temperature superconductivity through Meissner-effect and flux-pinning demonstrations, four-point probe measurements across the critical temperature, and Python-based plotting, curve fitting, and numerical analysis. Received grade 12.}

    \projectentry{Projekt Forskerspirer}
      {Developed an experimental research proposal on tuning the plasmon resonance frequency of semiconducting nanoparticles through charge-carrier-density control, involving doping, Raman scattering, and spectrophotometry. Received an honourable mention.}

    \projectentry{Tungsten --- author and maintainer}
      {Developed an open-source Neovim plugin that parses LaTeX mathematics and evaluates expressions directly in LaTeX documents using computational backends. Demonstrates systems thinking, technical documentation, release management, and complex problem decomposition.}

    \projectentry{DødsBo --- tractor-pulling vehicle}
      {Co-owned and rebuilt a garden-pulling tractor for a 350 kg competition class, including AutoCAD-based part design, metal fabrication, anti-tip brackets, weight-holder assemblies, drivetrain modification, and practical testing.}
  \end{connectedcontinued}
\end{minipage}

\end{document}
