\cvsection{Work Experience}


\begin{cventries}
  \cventry
    {Maintenance assistant} % Job title
    {LEGOLAND} % Organization
    {Billund Denmark} % Location
    {Dec. 2023 -- Dec. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Executed preventive maintenance and repairs on traffic school systems, including motors, gearboxes, and braking mechanisms.
        \item Managed and maintained over 70 animations in Miniland, ensuring a high quality of operation by diagnosing faults implementing durable fixes under time constraints.
        \item Worked across a broad range of electromechanical subsystems ranging from small-scale drivetrains to pump-systems and sensors.
      \end{cvitems}
    }

  \cventry
    {Facility Assistant} % Job title
    {LEGOLAND} % Organization
    {Billund, Denmark} % Location
    { Jun. -- Dec. 2022 \& Aug. -- Dec. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Installed and dismantled seasonal light fixtures, ensuring electrical connections and mounting structures met safety guidelines.
        \item Conducted inspections of 193 technical rooms, bridges, ladders, cooling systems, fire extinguishers and other critical park infrastructure to meet fire and safety regulations.
        \item Reported deviations clearly and followed up with relevant personel to ensure timely corrective actions.
      \end{cvitems}
    }

  \cventry
    {Tutor} % Job title
    {Syddansk Erhvervsskole} % Organization
    {Vejle, Denmark} % Location
    { Aug. 2021 -- Jun. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Peer tutoring; supported problem-solving and clear communication in all subjects. 
        \item Strengthened communication skills through adaptive explanations and feedback, both 1:1 and in small groups.
      \end{cvitems}
    }
\end{cventries}
