\cvsection{Project \& Research}

\begin{cventries}
  \cventry
    {Author and maintainer} % Affiliation/role
    {Tungsten} % Organization/group
    {Risskov, Denmark} % Location
    {Jan. 2025 -- Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item Design and maintain an open-source Neovim plugin enabling computational workflows inside \LaTeX\ documents via Wolfram Engine and Python.
      \item Translate user needs into implementable features, while maintaining a clear structure between components, interfaces, and documentation.
      \item Focus on reliability and usability through Test-driven-development, versioned changes, and documentation.
      \item Coordinated contributions/issues via GitHub (prioritization, triage, release planning).
      \end{cvitems}
    }

  \cventry
    {SOP-project on Superconductors (YBCO)} % Affiliation/role
    {Vejle Tekniske Gymnasium} % Organization/group
    {Vejle/Aalborg, Denmark} % Location
    {2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item Planned and executed a measurement workflow from hypothesis to verification, including setup constraints and experimental procedure.
      \item Performed four-point probe measurements through the critical temperature using cryogenic equipment.
      \item Analysed I--V data in Python to extract key parameters (e.g., critical temperature) and validate results against expected physical behaviour.
      \item Consolidated theory, methods, results, and limitations into a structured technical report with clear conclusions.
      \end{cvitems}
    }

  \cventry
    {Honorable Mention} % Affiliation/role
    {Projekt Forskerspirer -- University of Copenhagen} % Organization/group
    {Copenhagen, Denmark} % Location
    {Mar. 2022 - Nov. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item Conducted a supervised research project on doping of semiconducting nanoparticles to tune plasmon resonance.
      \item Collaborated with two PhD mentors (SDU), aligned scope and deliverables, and communicated progress and results clearly.
      \end{cvitems}
    }

  \cventry
    {Engineer} % Affiliation/role
    {DødsBo} % Organization/group
    {Vejle, Denmark} % Location
    {Oct. 2023 -- Nov. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
      \item Contributed to design, build, and the iterative improvement of a competition vehicle, balancing performance, reliability, and practical constraints.
      \item Diagnosed failures under time pressure and implemented robust fixes; coordinated hands-on work within the team to meet competition readiness.
      \item Achieved a top-10 finish in Jutland in a 350\,kg standard class.
      \end{cvitems}
    }
\end{cventries}
